\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Conclusion written

%% General intro

Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using fisheries data to infer
spatiotemporal dynamics of fish populations. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\citep{Martinez-Minaya2018}. Often data are aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes. Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatiotemporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\citep{Dunn2016}, understanding assumptions behind the data used - increasingly
a combination of logbook and positional information from vessel monitoring
systems - is vital to ensure measures are effective. \\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account.

EXPAND - relate to survey, commercial etc.. in Figure 2

@@

Bigger picture stuff::  LO, increasing desire for more nuanced spatiotemp
mgmt... Wider applicability: birds, wildlife ??

Study shows ....\\

This is important because .... \\

How we might apply this in future .... \\

>>>>

%% General intro
Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using fisheries data to infer
spatiotemporal dynamics of fish populations. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\citep{Martinez-Minaya2018}. Often data are aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes. Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatiotemporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\citep{Dunn2016}, understanding assumptions behind the data used - increasingly
a combination of logbook and positional information from vessel monitoring
systems - is vital to ensure measures are effective. \\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account. \\

Our simulation shows that, despite biases introduced through the fishing
process, the commercially derived data could still inform on the key spatial
patterns in the community structures where the fisheries occurred, which was
spatially limited due to the ``hotspots" of commercially valuable species being
fished. Similarly, despite the even spatial coverage the survey was able to
capture some of the same spatial patterns as the 'real population', but missed
others due to gaps between survey stations limiting spatial and temporal
coverage. This provides a challenge when modelling unsampled areas in inferring
species distribution maps, though these limitations may be overcome by
understanding the relationship between the species and habitat covariates where
these are known at unsampled locations \citep{Robinson2011}. \\

@@

MixFishSim provides a detailed simulation framework to explore the interaction
of multiple fisheries exploiting different fish populations. The framework
enables users to evaluate assumptions in modelling commercially derived data
through comparison to the true underlying dynamics at a fine spatial and
temporal scale.  Understanding these dynamics, the limitations of the data and
any potential biases that may be introduced when making inference on
spatiotemporal interactions will enable users to identify weaknesses in
modelling approaches and identity where data collection is needed to strengthen
inference. \\

Our application shows that inference on community dynamics may change depending
on the scale of data aggregation. There is an important balance in ensuring
that the data are sufficiently spatially and temporally disaggregated that the
main features of the data are captured, yet maintaining enough data coverage
that the features can be distinguished. We found in our application that there
was greater spatial heterogeneity than temporal heterogeneity and that when
using aggregated data to define spatial closures coarser temporal resolution
(months instead of weeks) could still achieve the same results in reducing
exploitation rates of a vulnerable species at the highest temporal resolution
data. Conversely, reducing the spatial resolution had a negative effect on the
effectiveness of the measures (though importantly, there was still some benefit
even with coarse spatial resolution). \\

While any findings are likely to be case specific, our findings emphasise the
need to understand population demographics, habitat use and movement rates in
designing any closure scenario based on observational sampling. This
information can then be used to set the bounds on data aggregation used in
modelling studies aimed at informing the management measures. \\

MixFishSim has numerous potential additional applications as it enables the
user to apply methods to a fisheries system where there is detailed
understanding of underlying spatiotemporal dynamics. This enables
identification of weaknesses or limitations which would not be possible
otherwise. In future, we recommend use of the framework to test hypothesis that
are otherwise unable to be analysed using real world data due to limitations of
data collection. That way the knowledge gained through simulation can inform
the future design of management measures.
